% Abstract
\vspace{1cm}
\begin{center}
\begin{minipage}{0.5\textwidth}
Through the theme; ”The incubator”, the group has developed a business model for a software platform, based on fishing, and connecting fishers via. the internet. This started with the problem definition; “How to obtain knowledge, in a foreign location?”. 
Thereafter the development of the software platform began through different techniques, which made the functions for the product clear. 

This resulted in a smartphone application, where users could rent out their fishing equipment, and also rent equipment from others. The income would be part of the renting fee. The application would also display businesses that wanted to advertise through the application. When the preliminary idea was done, a market analyse was carried out, to better understand the needs of the users. 

Here it was discovered that the renting function, was not the biggest opportunity for earning money, in change it would be better to offer the businesses a platform for making marketing and for selling. This opportunity came from speaking with physical and online shops, to hear about their way of advertising themselves. After the market analysis, the product's final requirements, was clarified to be an application, with multiple opportunities for fishers. Primarily the objectives of the application is to give easy access to go fishing, anywhere, anytime.

After this, a budget was estimated. In the operation budget, it can be seen, that the project has a negative bank balance in the first year, but it will be positive after the second year. To cover the negative bank balance in the start, a possibility could either be a bank loan or an investor. 
\end{minipage}	
\end{center}
