This section describes the creative methods, which has been used to develop the idea.
\subsection{Association Technique}
The associations technique has been used to solve the problem definition. The technique consists of the associations chain, focus, ideation and elaboration . After the association technique. 

\begin{table*}[t!]
\centering
\caption{Idea Assessment Table}
\label{tab:iass}
\begin{tabular}{|l|r|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\textbf{Idea Assessment Table. Point given 1-5, 5 is highest score}} & \multicolumn{4}{l|}{\textit{Idea number}} \\ \hline
Requirements: & \multicolumn{1}{l|}{\textit{Weights:}} & T:1 & E:3 & B:4 & C:6 \\ \hline
Can we earn money? & \textit{40 \%} & 13 & 9 & 7 & 5 \\ \hline
Does it give local knowledge to foreign people in new places. & \textit{15 \%} & 10 & 12 & 19 & 4 \\ \hline
Will people use it? & \textit{15 \%} & 14 & 9 & 14 & 10 \\ \hline
is it possible to create? & \textit{30 \%} & 20 & 11 & 19 & 20 \\ \hline
Is it sustainable? & \textit{20 \%} & 15 & 8 & 16 & 8 \\ \hline
\multicolumn{2}{|r|}{\textit{Total, with weights:}} & \cellcolor[HTML]{9AFF99}17.7 & \cellcolor[HTML]{FD6864}8.05 & \cellcolor[HTML]{FFFC9E}16.65 & \cellcolor[HTML]{FD6864}11.7 \\ \hline
\end{tabular}
\end{table*}

\subsubsection{Association Chain}
The associations chain initiates with one group member saying a random word, then the next member says the first word, they think of, when they hear the word. Thereafter the third member of the group says the first word they think of. This continues until there is about 20 words in the chain. After the chain is finished, the next part is the Focus part.

\subsubsection{Focus}
The focus question, is the same as the problem formulation namely; “How to obtain local knowledge, when in a foreign location”. The focus is important because it has a big influence in which direction the ideation is going. 

\subsubsection{Ideation}
Ideation is where the group discus every word, one by one and try to find a solution to the focus part, by using the words from the association chain. Here it is important to not set limitations to the answers, because it can limit the ideas, that will come out of this part.

\subsubsection{Elaboration}
At the elaboration we need to clarify our ideas from ideation. The best way to do that is to use sentences like: how can it be done, is it possible and how can we make it happen.

Ideas chosen with the Idea Sieve:
\begin{enumerate}
	\item List over places to rent fishing-equipment. 
	\item Eco friendly coloring to put in the ocean, to show the current, should disappear fast.
	\item A platform, that shows summer fitness possibilities, near you.
	\item A platform where people write down their sports and when they can meet.
	\item Platform to show where to buy/borrow a new EPI-pen.
	\item Platform for sharing leftover cake/food      
\end{enumerate}

Out of the six ideas,  there have been chosen four ideas to work with in the circle technique.

\subsection{Circle Technique}
The circle technique has three steps, the first is a short description of the ideas. When that is done the description is send to the next group member. In step two the group member is trying to make improvements to the idea . When every member has been looking for improvements, you move on to the final step. In the third and final step, all the improvements will be evaluated. The improvements, that the group find best are combined with the original idea (Appendix with the four ideas). After the ideas has been through the circle technique, the idea assessment phase is initiated. 

\textit{See the ideas created in the circle technique in appendix \ref{app:circ}.}

\subsection{Idea Assesment}
As seen in \autoref{tab:iass}, the ideas was rated in a rating system to assess our idea. First of all it was decided to choose five requirements. These requirements have to be something that describes a good idea to work further with. The requirements are not equally weighted, therefore each requirement was given a percentage to see how important they are. Idea T:1 got the highest score, that is why it was decided to change direction a bit from the initial thoughts about this project.

\subsubsection{Description of idea T:1}
{\noindent \textbf{T:1: List over places to rent fishing-equipment.}}
\begin{itemize}
	\item A platform where local people, and fishing enthusiasts can post the equipment, which they don’t currently use, it could be a fishing rod, but also knives and stuff like that, this could help other fishing enthusiasts to go fishing when on holiday, without the need to carry their equipment with them (as in they don’t need to carry their knives with them on the airplane.). 
	\item This could also cover other equipment based/heavy hobbies, like hunting, mountain climbing, camping, diving etc.
	\item The rentee (the one with the equipment) could ask for payment for renting, to cover wear and tear on the equipment.
	\item It should be possible to set a time period for how long time you are willing to rent-out your equipment. 
	\item Tutorial section to show how to make fishing equipment e.g. Spinning bait.
	\item Competetive: competes with local tourist based renting firms, but could be good (like uber).
	\item There have to be some rules/penalty about losing equipment, maybe a deposit.
	\item \textit{Earn money: take a percentage of the rent fee. }
\end{itemize}
\vspace{2em}



