As this project have been moving forward, there have been given response to ideas, therefore the original ideas have been changed over time, som that the renting equipment have been moved from the main feature to a secondary feature. The choice have been made because of response through the project and also surveys. The new main feature is focusing on getting shops to use the app to get customers. A way to increase the earn of the project could be to let customers buy from the shops through the app. That will make it possible to earn money on every order. 


Another reflection is about premium users, which was an idea in the start of the project, where the customers paid to gain extra features. But because of the low gain for it, the group expected that not many will pay a monthly pay for it. 


In the presentation of the product, there was good response about the fishing map, because today there are signs, that are no longer  maintained, therefore they can be hard to read and understand. This problem will the fishing map in the product solve and also make it cheaper, because there will be no need for the signs anymore.


Also in the presentation, there was talk about starting local or larger, by that it means, if the project should start on Funen or just start in all Danmark. By starting on Funen, there will be a slower start, but it is easier to avoid negative publicity, because there will be fewer users in the critical start up period. When the critical period is over, it will be more safe to expand to the rest of Denmark.