\begin{multicols}{2}
\footnotesize{
{\noindent \textbf{T:1: List over places to rent fishing-equipment.}}
\begin{itemize}
	\item A platform where local people, and fishing enthusiasts can post the equipment, which they don’t currently use, it could be a fishing rod, but also knives and stuff like that, this could help other fishing enthusiasts to go fishing when on holiday, without the need to carry their equipment with them (as in they don’t need to carry their knives with them on the airplane.). 
	\item This could also cover other equipment based/heavy hobbies, like hunting, mountain climbing, camping, diving etc.
	\item The rentee (the one with the equipment) could ask for payment for renting, to cover wear and tear on the equipment.
	\item It should be possible to set a time period for how long time you are willing to rent-out your equipment. 
	\item Tutorial section to show how to make fishing equipment e.g. Spinning bait.
	\item Competetive: competes with local tourist based renting firms, but could be good (like uber).
	\item There have to be some rules/penalty about losing equipment, maybe a deposit .
	\item \textit{Earn money: take a percentage of the rent fee. }
\end{itemize}
\vspace{2em}
{\noindent \textbf{E:3: A platform, that shows summer fitness possibilities, near you.}}
\begin{itemize}
	\item A platform to every fitness and sport lovers, so they easily can find a new place to workout. The users should rate the different places, so other users can find the best place for exactly their kind of sport/workout. There have to be a description to every fitness place.  
	\item This platform could include fitness centers, as well as public fitness parks, running groups, etc.
	\item Could also be expanded to finding “fitness buddies”, to train with.
	\item Could be expanded to track fitness stuff such as heart rate, repetitions, (distance) 
	\item Directions to the chosen fitness location.
	\item \textit{How to earn money:  when finding a fitness center, you get a discount price when showing that you have used the app, maybe the payment is done via the app. Part of the payment goes from the fitness center to the app.
}
\end{itemize}
\vspace{2em}
{\noindent \textbf{B:4: A platform where people write down their  sports and when they can meet.}}
\begin{itemize}
	\item A platform where people can write down their sport and when they can meet.
	\item This could be done via an app, with platforms for different sports.
	\item The idea could also be focused on one area, as the first initial idea.
	\item People can offer different kinds of sports and describe it, so the user can get interested, and read about the difficulty.
	\item And maybe the qualities of doing this sport, both physical, and psychical.
	\item The different activities could be rated (entertaining quality).
	\item Users could also create events (as 7in, soccer match at 3 p.m in the park), to inform other users that the event is going down, and they are able to join in, if they want to.
	\item Users could also be able to query for different things, if they want to know about a good jogging route, they can ask for one, and others can reply to the query, if enough people “support” (rate) the route, then the route could be shown on the map, so that other users don’t need to query about it in the future.
	\item \textit{User who provide knowledge of some sports, could charge a fee for sharing their knowledge, part of the fee could go the the app-devs.}
\end{itemize}
\vspace{2em}
{\noindent \textbf{C:6: Platform for sharing leftover cake/food}}
\begin{itemize}
	\item A great possibility to minimise food waste, great for students and people with low income, to get cheap or free desserts. Pictures of the dessert can be uploaded to show how much is left of the given dessert/cake. Localisation features to show cakes near you. Reviews of cake bakers, to indicate how skilled they are and to prevent people from poisoning other people.
	\item Competetive: it might interfere with the baker industry if people start to earn money.
	\item There is maybe already apps that are too close to this idea. 
	\item You have to know about the ingredients, if you are allergic of something.
	\item This could branch into other categories as well, Thomas can imagine, tap beer (from parties/events), food, and other stuff which may cause leftovers to occur.
	\item \textit{How to earn money: donations can be made for really good cakes (part goes to the app-company/part for the cake baker).}
\end{itemize}
}
\end{multicols}